EBASE manuscript

### 2023-01-22 manu-draft.qmd
table 1 and figs 1 and 2 redone with areal units

A preliminary assessment of the ability of EBASE to produce reasonable parameter estimates for $a$, $r$, and $b$ (@eq-ebase) was conducted using a simulated time series created with Fwoxy. These assessments evaluated if 1) EBASE estimates similar values for the known parameters, and 2) how the estimated values change with different model configurations. The simulated time series used inputs from an approximate one year of continuous data from Apalachicola Bay, Florida.  The input data were 2012 observations from February 22nd to December 19th at the Cat Point water quality monitoring station (29.7021$^{\circ}$ N, -84.8802$^{\circ}$ W) and included 15 minute observations of dissolved oxygen (mg/L), water temperature (C), and salinity (psu).  Continuous meteorological observations from the nearby East Bay station (29.7909$^{\circ}$ N, -84.8834$^{\circ}$ W, ~10km north of Cat Point) were combined with the water quality data at the same time step and included air temperature (C), wind speed (m/s), and PAR (mmol/m$^2$ as total per 15 minute observation). An oxygen time series was generated from Fwoxy using the inputs from Apalachicola Bay ([@fig-simapa]a), such that the simulated dissolved oxygen was created as close as possible to the observed given the inputs.  Known values for $a$ and $r$ parameters were returned for each time step of the simulated data, as well as all metabolic estimates for production, respiration, and gas exchange ([@fig-simapa]b and c).  The only parameter that could not be simulated by Fwoxy was $b$, which was set to 0.251 $\buni$ [@Wanninkhof14].

@@

![Simulated time series using the Fwoxy model for one year of continuous data at Apalachicola Bay.  Simulated input to EBASE was the (a) dissolved oxygen time series, with results compared to the (b) simulated $a$ parameter and (c) simulated metabolic estimates for production (P), respiration (R), and gas exchange (D).](figs/simapa.png){#fig-simapa}

>>>>

A preliminary assessment of the ability of EBASE to produce reasonable parameter estimates for $a$, $r$, and $b$ (@eq-ebase) was conducted using a simulated time series created with Fwoxy. These assessments evaluated if 1) EBASE estimates similar values for the known parameters, and 2) how the estimated values change with different model configurations. The simulated time series used inputs from an approximate one year of continuous data from Apalachicola Bay, Florida.  The input data were 2012 observations from February 22nd to December 19th at the Cat Point water quality monitoring station (29.7021$^{\circ}$ N, -84.8802$^{\circ}$ W) and included 15 minute observations of dissolved oxygen (mg/L), water temperature (C), and salinity (psu).  Continuous meteorological observations from the nearby East Bay station (29.7909$^{\circ}$ N, -84.8834$^{\circ}$ W, ~10km north of Cat Point) were combined with the water quality data at the same time step and included air temperature (C), wind speed (m/s), and PAR (mmol/m$^2$ as total per 15 minute observation). An oxygen time series was generated from Fwoxy using the inputs from Apalachicola Bay ([@fig-synapa]a), such that the simulated dissolved oxygen was created as close as possible to the observed given the inputs.  Known values for $a$ and $r$ parameters were returned for each time step of the simulated data, as well as all metabolic estimates for production, respiration, and gas exchange ([@fig-synapa]b and c).  The only parameter that could not be simulated by Fwoxy was $b$, which was set to 0.251 $\buni$ [@Wanninkhof14].

@@

![Synthetic time series using the Fwoxy model for one year of continuous data at Apalachicola Bay.  Synthetic input to EBASE was the (a) dissolved oxygen time series, with results compared to the (b) simulated $a$ parameter and (c) simulated metabolic estimates for production (P), respiration (R), and gas exchange (D).  The $a$ parameter is shown as an areal value for comparison with the metabolic results.](figs/synapa.png){#fig-synapa}
